\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{palatino}
\usepackage{geometry}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{titlesec}  % For custom section titles
\usepackage{enumitem}  % For item spacing
\usepackage{parskip}   % No indentation for new paragraphs

% Set page margins
\geometry{
  top=1.2in,
  bottom=1.2in,
  left=1in,
  right=1in
}

% Hyperlink styling
\hypersetup{
  colorlinks=true,
  urlcolor=blue
}

% No page number
\pagestyle{empty}

% Section formatting
\titleformat{\section}{
  \Large\bfseries
}{}{0em}{}[\titlerule]

% Reduce spacing between items
\setlist[itemize]{itemsep=3pt, topsep=3pt}

\begin{document}

\begin{center}
  {\Huge \textbf{Sumit Thakkar}}\\[8pt]
  \faPhone \ +91 63550 61859 \quad
  \faEnvelope \ \href{mailto:thakkarsumit1112@gmail.com}{thakkarsumit1112@gmail.com} \quad
  \faLinkedinSquare \ \href{https://linkedin.com/sumitthakkar}{linkedin.com/sumitthakkar}
\end{center}

\vspace{0.5cm}

\section*{Education}

\textbf{Gujarat University}, Ahmedabad, India \\
\textit{Master of Computer Application – First Class} \hfill \textbf{Expected:} June 2024

\vspace{0.2cm}

\textbf{Shree V R Patel College of Commerce, HNGU}, Gujarat, India \\
\textit{Bachelor of Commerce – First Class Distinction} \hfill \textbf{Completed:} May 2022

\section*{Experience}

\textbf{Junior Data Engineer} \hfill July 2024 – Present \\
\textit{Inferenz Tech Pvt. Ltd., Ahmedabad} 
\begin{itemize}
  \item Developed and optimized SQL stored procedures for efficient data management.
  \item Analyzed API responses and created actionable reports.
  \item Transformed semi-structured data in a snowflake.
  \item Collaborated with global teams to troubleshoot transmission failures.
  \item Created a CI/CD pipeline in a project.
  \item Hands on experience with snowpark, databricks, ADF, Azure Functions.
\end{itemize}
\vspace{0.8cm}
\textbf{Junior Data Engineer - Intern} \hfill Jan 2024 – June 2024 \\
\textit{Inferenz Tech Pvt. Ltd., Ahmedabad} 
\begin{itemize}
  \item Data cleaning and transformation performed using SQL and Python (Pandas).
  \item Built web scrapers using Selenium, BeautifulSoup (bs4), and Requests libraries in Python.
  \item Gained hands-on experience with NoSQL databases such as MongoDB and Amazon DynamoDB.
  \item Completed Snowflake badges focused on SaaS Warehouse Management and Big Data Analysis.
  \item Used Git and GitHub for version control and collaborative development.
  \item Applied Infrastructure as Code concepts using Terraform.
  \item Completed AWS Cloud Quest: Cloud Practitioner certification.
\end{itemize}
\vspace{0.8cm}

\textbf{Software Developer Intern} \hfill Aug 2023 – Oct 2023 \\
\textit{Code Novus Tech, Remote}
\begin{itemize}
  \item WordPress websites maintained for optimal performance.
  \item Designed landing pages for marketing campaigns.
  \item Collaborated cross-functionally for design and functionality improvements.
\end{itemize}

% \section*{Projects}

% \textbf{API Data Analysis and Transformation} \\
% \textit{Python, SQL, Snowflake, API Integration}
% \begin{itemize}
%   \item Data extracted and processed from external APIs.
%   \item Structured insights using SQL views and procedures.
% \end{itemize}

% \textbf{Website Optimization \& Enhancement} \\
% \textit{WordPress, HTML, CSS, JavaScript}
% \begin{itemize}
%   \item Enhanced site performance, responsiveness, and consistency in user interface.
%   \item Expanded features using plugin integrations.
% \end{itemize}

\section*{Certifications}

\begin{itemize}
  \item Neo4j Certified Professional – \textit{Neo4j}, Mar 2025
  \item Databricks Fundamentals – \textit{Databricks}, Jan 2025
  \item AWS Cloud Quest: Cloud Practitioner – \textit{AWS}, June 2024
  \item Snowflake Data Engineering Workshop – \textit{Snowflake}, Apr 2024
  \item Snowflake Warehousing, Marketplace, Application Builders, and Data Lake Workshops – Apr 2024
\end{itemize}

\section*{Technical Skills}

\begin{tabular}{@{}ll}
\textbf{Programming}       & Python, SQL \\[6pt]
\textbf{Databases}         & Snowflake, MySQL, MongoDB, Neo4j \\[6pt]
\textbf{Cloud Platforms}   & AWS (S3, IAM, EC2, RDS, DynamoDB), Azure (ADF, Azure Functions, Blob Storage) \\[6pt]
\textbf{Data Engineering}  & Stored Procedures, API Integration, SQL Views, Data Governance \\[6pt]
\textbf{Visualization}     & Matplotlib \\[6pt]
\textbf{Version Control}   & Git, GitHub \\[6pt]
\textbf{Soft Skills}       & Problem-solving, Analytical Thinking, Communication
\end{tabular}




\end{document}
